Modeling the Circumnuclear Mediums and Accetion Rates of Quiescent Supermassive Black Holes

### 2014-11-15 ms.tex
Reincorporating my changes for the conductivity.

The importance of conductive heating can be estimated by comparing its
magnitude to that of wind heating, viz.~
\begin{eqnarray} \left.\frac{\nabla\cdot(\kappa \nabla T)}{q v_{\rm
w}^{2}/2}\right|_{r_{\rm s}} &\sim& \frac{2t_{\rm h}\kappa_0
T^{7/2}}{r_{\rm s}^{2}\eta \rho_{\star}(r_{\rm s}) v_{\rm w}^{2}}
\nonumber \\ &\sim&
0.5\left(\frac{\eta}{0.1}\right)^{-1}\left(\frac{r_{\rm s}}{r_{\rm
soi}}\right)^{-\beta} v_{500}^{3}\chi^{3},
\end{eqnarray}

where we have approximated $\nabla^{2} \sim 1/r_{\rm st}^{2}$ and in the second equality have made use of equations (\ref{eq:Tanalytic}), (\ref{eq:stag_simple}) and have approximated $4\pi r_{\rm s}^{3}\rho_{\star}(r_{\rm s}) \approx M_{\bullet}(r_{\rm s}/r_{\rm soi})^{\beta}$ with $\beta \approx 1-2$.  We thus see that conductive heating is important near the stagnation radius for high values of $v_{\rm w} \gtrsim 500$ km s$^{-1}$ and $\eta \gtrsim 0.1$, but that it is safely neglected to first order for lower heating rates.

@@

\begin{eqnarray}
  \dot{M} &=& \frac{\eta \Menc(\rs)}{\th} \nonumber \\
&\approx&
  \begin{cases}
    1.5 \times 10^{-3} M_{\bullet,8}^{1.76}
    \chi^{-3.8} v_{500}^{-3.8}  \eta \Msun \, \pyear& \text{core} \\
    2.6 \times 10^{-3} \Mbheight^{1.48} 
    \chi^{-2.4} v_{500}^{-2.4}  \eta \Msun \, \pyear  & \text{cusp}, 
  \end{cases}
  \label{eq:mdot_analytic}
\end{eqnarray}

>>>>

The importance of conductive heating can be estimated by comparing its
magnitude to that of wind heating, viz.~
\begin{align} \left.\frac{\nabla\cdot(\kappa \nabla T)}{q v_{\rm
w}^{2}/2}\right|_{r_{\rm s}} &\sim \frac{2t_{\rm h}\kappa_0
T^{7/2}}{r_{\rm s}^{2}\eta \rho_{\star}(r_{\rm s}) v_{\rm w}^{2}}
\nonumber \\ &\sim
10.5 \left(\frac{\eta}{0.1}\right)^{-1}\left(\frac{r_{\rm s}}{r_{\rm
soi}}\right)^{-\beta} v_{500}^{9}\chi^{9} \nonumber \\ &\sim
4.53 \, 0.43^{\beta-1} \left(\frac{\eta}{0.1}\right)^{-1}
M_{\bullet,8}^{-1.2+0.4\beta} v_{500}^{9-2\beta}\chi^{9-2\beta}
\label{eq:condRatio1}
\end{align}

where we have approximated $\nabla^{2} \sim 1/r_{\rm st}^{2}$ and in
the second equality have made use of equations (\ref{eq:Tanalytic}),
(\ref{eq:stag_simple}) and have approximated $4\pi r_{\rm
  s}^{3}\rho_{\star}(r_{\rm s}) \approx M_{\bullet}(r_{\rm s}/r_{\rm
  soi})^{\beta}$ with $\beta \approx 1-2$.  We thus see that
conductive heating is important near the stagnation radius for high
values of $v_{\rm w} \gtrsim 500$ km s$^{-1}$ and $\eta \gtrsim 0.1$,
but that it is safely neglected to first order for lower heating
rates. {\bf AG:Should probably include mass. Although this is tricky
  as cusp and core galaxies have opposite dependencies on mass.}

In fact, for high heating rates conductive heating is less important
than equation~\eqref{eq:condRatio1} would suggest due to the effects
of saturation. In this regime the importance of conductive heating can
be estimated the conductive flux in equation~\eqref{eq:condRatio1}
with its saturated value.
\begin{eqnarray} \left.\frac{\nabla\cdot(f_{\rm cond})}{q v_{\rm
w}^{2}/2}\right|_{r_{\rm s}} &\sim& \frac{2t_{\rm h} \phi \rho(\rs) c_s(\rs)^3}{r_{\rm s}^{2}\eta \rho_{\star}(r_{\rm s}) v_{\rm w}^{2}}
\nonumber \\ &\sim&
\frac{10 \phi}{2-\Gamma}, \label{eq:condRatio}
\end{eqnarray}

where we have approximated $\nabla \sim 1/r_{\rm st}$ and in the
second equality have made use of equations (\ref{eq:Tanalytic}),
(\ref{eq:stag_simple}), and (\ref{eq:rhors}). The stellar density is
assumed to be a power law $\rho_{\star}=\frac{\Mbh
  \left(2-\Gamma\right)}{4 \pi \rsoi^3}
\left(\frac{\rs}{\rsoi}\right)^{-1-\Gamma}$.

From the saturated value of the conductive heat flux we have found an
upper bound on the ratio of the rate of heating to the rate of heat
conduction in equation~\eqref{eq:condRatio}.  For $\phi\simeq 1$, the
conductive flux could be quite important. However, the value of $\phi$
depends various details from plasma physics, and could plausibly be an
order of magnitude smaller. In light of these uncertainties we neglect
the effect of the conductive flux.

@@

\begin{eqnarray}
  \dot{M} &=& \frac{\eta \Menc(\rs)}{\th} \nonumber \\
&\approx&
  \begin{cases}
    1.5 \times 10^{-3} M_{\bullet,8}^{1.76}
    \chi^{-3.8} v_{500}^{-3.8}  \eta \Msun \, \pyear& \text{core} \\
    2.6 \times 10^{-3} M_{\bullet,8}^{1.48} 
    \chi^{-2.4} v_{500}^{-2.4}  \eta \Msun \, \pyear  & \text{cusp}, 
  \end{cases}
  \label{eq:mdot_analytic}
\end{eqnarray}
